Quasi-Monte Carlo Methods: What, Why, and How?

### 2025-01-08 HickernellMCQMC2024_QMCTutorial.tex
Updates from Overleaf

\begin{figure}
	\centering
	\includegraphics[width =10cm]{\figpath/n_is_16777216_d_is_6_n_rep_is_50_KeisterErrors.pdf}
	\caption{The relative error of approximationg $\mu$ defined in \eqref{eq:keisterC} by the sample mean, $\hat{\mu}_n$ defined in \eqref{eq:sample_mean} for various choices of nodes, $\bsx_0, \bsx_1, \ldots$.  Grids have the largest error and LD nodes have the smallest error. \label{fig:keister-err}}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[width =10cm]{\figpath/n_is_16777216_d_is_6_n_rep_is_50_KeisterErrors.pdf}
	\caption{The relative error of approximating $\mu$ defined in \eqref{eq:keisterC} by the sample mean, $\hat{\mu}_n$ defined in \eqref{eq:sample_mean} for various choices of nodes, $\bsx_0, \bsx_1, \ldots$.  Grids have the largest error and LD nodes have the smallest error. \label{fig:keister-err}}
\end{figure}
